A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-12-05 paper/paper.tex
paper: minor polish

\subsection{Formal construction in intensional type theory\label{sec:itt}}
We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will soon explain.

@@

\bibliographystyle{alpha}
\bibliography{paper}

>>>>

\subsection{Formal construction in intensional type theory\label{sec:itt}}
\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}

We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will explain shortly.

@@

\newpage
\bibliographystyle{alpha}
\bibliography{paper}
